Data Management \\ and LSST Special Programs

### 2022-02-21 ap_docrev.tex
update hardbounds pointing

@@

>>>>

In Section 3.6.3.1, ``Absolute Pointing", OSS-REQ-0298\ossreq{0298} specifies that {\it ``the LSST shall point to a defined set of sky coordinates with an RMS accuracy
of" 2 arcseconds ({\tt absPointErr}\reqparam{absPointErr}).

@@

In Section 3.6.3.5, ``Offset Pointing", OSS-REQ-0302\ossreq{0302} specifies that {\it ``the LSST shall be capable of offset pointing within a single field-of-view with a precision of no more than" 0.2 arcseconds ({\tt offsetPointingErr}\reqparam{offsetPointingErr}).

In Section 3.6.3.6, ``Open Loop Tracking", OSS-REQ-0303\ossreq{0303} specifies that {\it ``The LSST shall be capable of open loop tracking without the assistance of real
time optical feedback to an accuracy of"} 1.0 arcseconds ({\tt openTrackErr}\reqparam{openTrackErr}) {\it ``over any 10 minute duration during normal night time operations"}.
Note that the open loop tracking requirement is \emph{without guiding}.

In Section 3.6.3.8, ``Guiding", OSS-REQ-0305\ossreq{0305} specifies that {\it ``the LSST system shall improve the tracking of the optical system to the sky by means of active guiding over the whole accessible sky"}.

### 2022-02-21 ap_hardbounds.tex
update hardbounds pointing

\subsection{Inter-Image Time}
Images with exposure times $<15$ seconds {\it might} still have to be separated by $15$ seconds for thermal tolerance; i.e., the minimum readout rate might be one image every $15$ seconds, regardless of exposure time (OSS-REQ-0291; \citeds{LSE-30}).
The $15$ interval between images is a potential hardware boundary on the potential diversity of data products.

@@

\subsection{Telescope Tracking}
The requirement that the LSST system be able to perform non-sidereal tracking is set by OSS-REQ-0380 in \citeds{LSE-30}.
This capability will include angular rates of up to 220 arcseconds per second in both azimuth and elevation.

>>>>

\subsection{Inter-Image Time}
Images with exposure times $<15$ seconds {\it might} still have to be separated by $15$ seconds for thermal tolerance; i.e., the minimum readout rate might be one image every $15$ seconds, regardless of exposure time (OSS-REQ-0291; \citeds{LSE-30}).
This potential $15$ interval between images is also a potential hardware boundary on the potential diversity of data products.
Current (2022) testing of the camera system indicates that imposing waits between short exposures will not be necessary

@@

\subsection{Pointing and Sidereal Tracking}
The specifications for the telescope's pointing and tracking in \citeds{LSE-30} indicate that $<$0.2 arcsecond precision in field pointing (OSS-REQ-0302) and $<$1 arcsecond in open-loop tracking (OSS-REQ-0303) would not be possible, but guiding would improve the latter (OSS-REQ-0305).
Furthermore, obtaining the \emph{exact same} alignment of the pixel grid in RA-Dec {\it ``would put demands on the camera rotator that were not planned"}\footnote{As per C. Claver's comments in ticket DM-12573.}.

\subsection{Non-Sidereal Tracking}
The requirement that the LSST system be able to perform non-sidereal tracking is set by OSS-REQ-0380 in \citeds{LSE-30}.
This capability will include angular rates of up to 220 arcseconds per second in both azimuth and elevation.
